NCAM Explorer

### 2020-03-14 inst/rmd/trends.Rmd
Revamped NCAM explorer

---
title: "NCAM Explorer"
output: flexdashboard::flex_dashboard
always_allow_html: yes
---

<style>
/* list */
li {
line-height: 30px;
}
</style>

```{r setup, echo=FALSE}
library(plotly)
library(Matrix)
library(knitr)
library(data.table)
library(dplyr)
library(webshot)
knitr::opts_knit$set(root.dir = tmp$output_dir)
knitr::opts_chunk$set(echo = FALSE, fig.height = 7, fig.width = 8)
```

```{r data, include=FALSE}

cols <-  viridis::viridis(4)[c(2, 3, 1, 4)]
cols_rgb <-  paste0("rgb(", apply(col2rgb(cols), 2, paste, collapse = ","), ")")
fit <- tmp$fit # temp object from vis_fit function
if (!is.null(tmp$comp)) { comp <- tmp$comp }
if (!is.null(tmp$last)) { last <- tmp$last }
est <- as.list(fit$sd.rep, "Est")
sd <- as.list(fit$sd.rep, "Std")
tabs <- tidy_model(fit)
if (!is.null(tmp$comp)) { comp_tabs <- tidy_model(model_list = comp) }
if (!is.null(tmp$last)) { last_tabs <- tidy_model(tmp$last) }
if (!is.null(fit$retro)) { retro_tabs <- tidy_retro(fit) } 
min_year <- min(fit$tmb.data$years)
max_year <- max(fit$tmb.data$years)
ages <- fit$tmb.data$ages
years <- fit$tmb.data$years
years_plus1 <- fit$tmb.data$years_plus1

## helper functions for nice Rmarkdown text
text_range <- function(x) paste(range(x), collapse = "-")
text_c <- function(x) {
  paste0(paste(x[-length(x)], collapse = ", "), ", and ", x[length(x)])
}
text_units <- function(x) {
  if (x >= 1000000) return(paste0(round(x / 1000000), "M"))
  if (x >= 1000) return(paste0(round(x / 1000), "k"))
  if (x < 1000) return(as.character(round(x)))
}

Background
================================================================================

### NCAM

<h1>NCAM: A state-space stock assessment model for Northern cod</h1>

ax <- list(
  title = "",
  zeroline = FALSE,
  showline = FALSE,
  showticklabels = FALSE,
  showgrid = FALSE
)

xy <- approx(x = years_plus1, y = fit$rep$abundance + 1000000, n = 50)
plot_ly(x = xy$x, y = xy$y, hoverinfo = "none",
        fillcolor = 'rgba(49, 104, 142, 0.3)',
        type = 'scatter', mode = 'none', fill = 'tozeroy', showlegend = FALSE) %>%
  add_trace() %>%
  layout(xaxis = ax, yaxis = c(list(range = c(0, max(xy$y))), ax),
         margin = list(l = 0, r = 0, b = 0, t = 0, pad = 0)) %>% 
  plotly::config(displayModeBar = FALSE)

### General

- An *integrated* *state-space* population dynamics model
- *Integrated*
    - Uses as much information as possible
- *State-space*
    - Includes process and observation equations + error
    - Population processes are informed by observations from multiple sources
    - Process errors are necessary for realistic stochastic projections

### Data inputs

- Reported landings (`r text_range(years)`)
- Catch-at-age information (`r text_range(years)`)
- Reported landings by month (`r text_range(years)`)
- Offshore research vessel (RV) survey indices (`r text_range(c(1983, max(years)))`)
- Inshore sentinel (SN) gillnet survey indices (`r text_range(fit$tmb.data$SN_years)`)
- Inshore acoustic biomass surveys and age composition data from Smith Sound (SS; `r text_range(fit$tmb.data$SS_years)`)
- Tagging data (`r text_range(years)`)

### Biological inputs

- RV survey data were used fit cohort-based models of:
   - Proportion mature at age
   - Beginning of year and mid-year stock weights at age
- Baseline natural mortality (M) values

plot_ly(x = years, y = ages, z = fit$rep$M_matrix, height = 400, width = 500) %>%
  add_surface() %>%
  colorbar(title = "Mshift") %>%
  layout(scene = list(
    xaxis = list(title = "Year"),
    yaxis = list(title = "Age"),
    zaxis = list(title = "Mshift")
  ))

### Partial catches

- User sets lower and upper bounds on total catch weight
- Bounds are used via a censored likelihood

plot_ly(x = years, y = fit$tmb.data$LRL, height = 300, width = 500) %>%
  add_lines(name = "Lower", color = I(cols[1])) %>%
  add_lines(y = fit$tmb.data$LRU, name = "Upper", color = I(cols[2])) %>%
  add_lines(y = rep(1, length(years)), color = I("black"),
            line = list(width = 1, dash = "dot"), showlegend = FALSE) %>%
  layout(yaxis = list(title = "Catch multiplier"),
         xaxis = list(title = "Year"))

### Change in Q

- A shift in Q was assumed for the offshore RV survey
- A variable portion of the stock is assumed to occupy Smith Sound between `r text_range(fit$tmb.data$SS_years)`
- Q for the inshore sentinel survey was assumed to follow a random walk
    - Done to account for potential changes in migration patterns

### Tagging data

- Age of tagged fish estimated from length-at-release using a spatiotemporal Von Bertalanffy growth model
- Applies adjustments for tagging mortality, tag loss and reporting rates
- Reporting rates estimated by an external model using the high-reward tag data collected since 1997
- The Baranov catch equation was applied to age-based tag survivors
- Assumes that initial fishing mortality experienced by fish in each experiment are random deviations from the fishing mortality experienced by the whole stock

### References

Cadigan, N. 2015. A state-space stock assessment model for Northern cod, including under-reported catches and variable natural mortality rates. Canadian Journal of Fisheries and Aquatic Sciences 73 (2). NRC Research Press: 296-308.

Cadigan, N. 2016. Updates to a Northern cod (*Gadus morhua*) state-space integrated assessment model. DFO Can. Sci. Advis. Sec. Res. Doc. 2016/022. v + 58 p.

Catch
================================================================================

### Landings

plot_landings(fit)

> Y-axes in log scale

### Numbers at age

d <- tidy_mats(list(obs = t(inputs$catch.num[as.character(years), as.character(ages)]),
                    pred = fit$rep$pred_catch),
               ages = ages, years = years)
d$cohort <- factor(d$year - d$age)
d$age <- factor(d$age)

facet_obs_pred(d, by = "age", type = "log",
               which = c(2, 8, 3, 9, 4, 10, 5, 11, 6, 12, 7, 13), # done to order by column
               nrows = 6, ylab = "Proportion",
               obs_col = cols[2], pred_col = cols[1]) %>%
  layout(yaxis = list(rangemode = "tozero"))

> Y-axes in log scale; also note that model fits to composition - this plot is included for illustration

### Predictions by age

```{r}
plot_obs_pred(data = d, showlegend = TRUE, 
              type = "log", group = "age",
              group_cols = viridis::viridis(nlevels(d$age), 
                                            direction = 1, end = 0.8),
              ylab = "Numbers")
```

> Y-axes in log scale; also note that model fits to composition - this plot is included for illustration

### Predictions by cohort

```{r}
plot_obs_pred(data = d, showlegend = TRUE, 
              type = "log", group = "cohort",
              group_cols = viridis::viridis(nlevels(d$cohort), 
                                            direction = 1, end = 0.8),
              ylab = "Numbers")
```

> Y-axes in log scale; also note that model fits to composition - this plot is included for illustration

### Numbers at age surface

```{r}
plot_surface(mat = t(inputs$catch.num[as.character(years), as.character(ages)]), 
             ages = ages, years = years, name = "N")
```

> Note: model fits to composition - this plot is included for illustration

### Proportions at age

d <- tidy_mats(list(obs = fit$tmb.data$catch_prop,
                    pred = fit$rep$pred_prop_catch),
               ages = ages, years = years)
d$cohort <- factor(d$year - d$age)
d$age <- factor(d$age)

facet_obs_pred(d, by = "age",
               which = c(2, 8, 3, 9, 4, 10, 5, 11, 6, 12, 7, 13), # done to order by column
               nrows = 6, ylab = "Proportion",
               obs_col = cols[2], pred_col = cols[1]) %>%
  layout(yaxis = list(rangemode = "tozero"))

### Fits by age

```{r}
plot_obs_pred(data = d, showlegend = TRUE, 
              type = "linear", group = "age",
              group_cols = viridis::viridis(nlevels(d$age), 
                                            direction = 1, end = 0.8),
              ylab = "Proportion", stack_group = TRUE)
```

> Note: values are stacked

### Fits by cohort

```{r}
plot_obs_pred(data = d, showlegend = TRUE, 
              type = "linear", group = "cohort",
              group_cols = viridis::viridis(nlevels(d$cohort), 
                                            direction = 1, end = 0.8),
              ylab = "Proportion", stack_group = TRUE)
```

> Note: values are stacked

### Residuals by year, cohort, age and expected values

d <- tidy_mats(list(res = fit$rep$CA_resid,
                    fit = fit$rep$pred_crl),
               ages = ages[-length(ages)], years = years)
d$cohort <- d$year - d$age
d$rec <- seq(nrow(d))
plot_resid(d, col = cols[1])

> based on continuation ratio logits

### Proportions at age surface

```{r}
plot_surface(mat = fit$rep$pred_prop_catch, ages = ages, years = years, name = "P")
```

RV Survey {data-navmenu="Surveys"}
================================================================================

### RV survey index

obs <- colSums(fit$tmb.data$est_wt * fit$tmb.data$RV_index * fit$tmb.data$trawl_units)
pred <- colSums(fit$tmb.data$est_wt * exp(fit$rep$Elog_RV_index) * fit$tmb.data$trawl_units)
obs[obs == 0] <- NA
pred[pred == 0] <- NA
d <- data.frame(year = years, obs = obs, pred = pred)

# ## RV biomass
# obs <- colSums(fit$tmb.data$RV_index * fit$tmb.data$trawl_units * fit$tmb.data$weight)
# pred <- colSums(exp(fit$rep$Elog_RV_index) * fit$tmb.data$trawl_units * fit$tmb.data$weight)
# d <- data.frame(year = years, obs = obs, pred = pred)
# write.table(d, file = "clipboard", sep = "\t", row.names = FALSE, quote = FALSE)

plot_obs_pred(d, obs_col = cols[2], pred_col = cols[1], ylab = "RV survey index",
              showlegend = TRUE, type = "log")

> Y-axes in log scale

### Standardized log residuals

d <- tidy_mats(list(res = fit$rep$RV_resid,
                    zero = fit$tmb.data$ind_zero,
                    wt = fit$tmb.data$est_wt),
               ages = ages, years = years)
d <- d[d$wt == 1, ]
bubble_plot(d)

### RV survey index at age

d <- tidy_mats(list(obs = fit$tmb.data$RV_index,
                    pred = exp(fit$rep$Elog_RV_index),
                    wt = fit$tmb.data$est_wt),
               ages = ages, years = years)
d$obs[d$wt == 0] <- NA
d$pred[d$wt == 0] <- NA
d$cohort <- factor(d$year - d$age)
d$age <- factor(d$age)

facet_obs_pred(d, by = "age",
               which = c(2, 8, 3, 9, 4, 10, 5, 11, 6, 12, 7, 13), # done to order by column
               nrows = 6, ylab = "Mean numbers per tow",
               obs_col = cols[2], pred_col = cols[1], type = "log")

> Y-axes in log scale

### Fits by age

```{r}
plot_obs_pred(data = d, showlegend = TRUE, 
              type = "log", group = "age",
              group_cols = viridis::viridis(nlevels(d$age), 
                                            direction = 1, end = 0.8),
              ylab = "Mean numbers per tow")
```

> Y-axes in log scale

### Fits by cohort

```{r}
plot_obs_pred(data = d, showlegend = TRUE,
              type = "log", group = "cohort",
              group_cols = viridis::viridis(nlevels(d$cohort), 
                                            direction = -1, end = 0.8),
              ylab = "Mean numbers per tow")
```

> Y-axes in log scale

### Residuals by year, cohort, age and expected values

d <- tidy_mats(list(res = fit$rep$RV_resid,
                    keep = fit$tmb.data$ind_zero == 0 & fit$tmb.data$est_wt == 1,
                    fit = fit$rep$Elog_RV_index),
               ages = ages, years = years)
d <- d[d$keep, ]
d$cohort <- d$year - d$age
d$rec <- seq(nrow(d))
plot_resid(d, col = cols[1])

SN Survey {data-navmenu="Surveys"}
================================================================================

### Sentinel gillnet survey index

obs <- colSums(fit$tmb.data$SN_GN_index)
pred <- colSums(exp(fit$rep$Elog_SN_GN_index))
d <- data.frame(year = fit$tmb.data$SN_years, obs = obs, pred = pred)

plot_obs_pred(d, obs_col = cols[2], pred_col = cols[1], ylab = "Sentinel survey index",
              showlegend = TRUE, type = "log")

> Y-axes in log scale

### Standardized log residuals

d <- tidy_mat(fit$rep$log_SN_GN_resid,
              ages = fit$tmb.data$SN_ages,
              years = fit$tmb.data$SN_years, value = "res")
bubble_plot(d)

### Sentinel gillnet survey index at age

d <- tidy_mats(list(obs = fit$tmb.data$SN_GN_index,
                    pred = exp(fit$rep$Elog_SN_GN_index)),
               ages = fit$tmb.data$SN_ages, years = fit$tmb.data$SN_years)
d$cohort <- factor(d$year - d$age)
d$age <- factor(d$age)

facet_obs_pred(d, by = "age",
               which = c(3, 7, 4, 8, 5, 9, 6, 10), # done to order by column
               nrows = 4, ylab = "Sentinel survey index",
               obs_col = cols[2], pred_col = cols[1], type = "log")

> Y-axes in log scale

### Fits by age

```{r}
plot_obs_pred(data = d, showlegend = TRUE, 
              type = "log", group = "age",
              group_cols = viridis::viridis(nlevels(d$age), 
                                            direction = 1, end = 0.8),
              ylab = "Sentinel survey index")
```

> Y-axes in log scale

### Fits by cohort

```{r}
plot_obs_pred(data = d, showlegend = TRUE,
              type = "log", group = "cohort",
              group_cols = viridis::viridis(nlevels(d$cohort), 
                                            direction = -1, end = 0.8),
              ylab = "Sentinel survey index")
```

> Y-axes in log scale

### Residuals by year, cohort, age and expected values

d <- tidy_mats(list(res = fit$rep$log_SN_GN_resid,
                    fit = fit$rep$Elog_SN_GN_index),
               ages = fit$tmb.data$SN_ages,
               years = fit$tmb.data$SN_years)
d$cohort <- d$year - d$age
d$rec <- seq(nrow(d))
plot_resid(d, col = cols[1])

SS Survey {data-navmenu="Surveys"}
================================================================================

### Smith sound acoustic biomass estimates

d <- data.frame(year = fit$tmb.data$SS_bms_years,
                obs = fit$tmb.data$SSbms,
                pred = fit$rep$ESSbms)
plot_obs_pred(d, obs_col = cols[2], pred_col = cols[1], ylab = "Biomass (t)",
              showlegend = TRUE)

### Standardized log residuals

d <- tidy_mat(fit$rep$SS_agecomps_resid_std,
              ages = fit$tmb.data$SS_ages,
              years = fit$tmb.data$SS_age_years, value = "res")
bubble_plot(d)

### Smith Sound trawl numbers at age

d <- tidy_mats(list(obs = fit$tmb.data$SS_agecomps,
                    pred = fit$rep$ESS_agecomps),
               ages = fit$tmb.data$SS_ages,
               years = fit$tmb.data$SS_age_years)
facet_obs_pred(d, by = "age",
               which = c(2, 8, 3, 9, 4, 10, 5, 11, 6, 12, 7, 13), # done to order by column
               nrows = 6, ylab = "Numbers caught", rangemode = "tozero",
               obs_col = cols[2], pred_col = cols[1])

### Residuals by year, cohort, age and expected values

d <- tidy_mats(list(res = fit$rep$SS_agecomps_resid_std,
                    fit = fit$rep$ESS_agecomps),
               ages = fit$tmb.data$SS_ages,
               years = fit$tmb.data$SS_age_years)
d$cohort <- d$year - d$age
d$rec <- seq(nrow(d))
plot_resid(d, col = cols[1])

Tagging {data-orientation=rows}
================================================================================

## Prep tag data and fits
tag_dat <- data.frame(
  exp = c(fit$tmb.data$old_tag_exp, fit$tmb.data$tag_exp),
  n_rel = c(fit$tmb.data$old_N_rel, fit$tmb.data$N_rel),
  rel_year = c(fit$tmb.data$old_rel_year, fit$tmb.data$rel_year) + min(years),
  cap_year = c(fit$tmb.data$old_cap_year, fit$tmb.data$cap_year) + min(years),
  age = c(fit$tmb.data$old_tag_age, fit$tmb.data$tag_age),
  pred = c(fit$rep$old_tag_report, fit$rep$tag_report),
  obs = c(fit$tmb.data$old_N_cap, fit$tmb.data$N_cap),
  res = c(fit$rep$old_tag_std_resid, fit$rep$tag_std_resid),
  period = c(rep("pre 1996", length(fit$tmb.data$old_tag_exp)),
             rep("post 1996", length(fit$tmb.data$tag_exp)))
)
tag_dat$delay <- tag_dat$cap_year - tag_dat$rel_year
tag_dat$text <- paste("exp:", tag_dat$exp, "</br>",
                      "age:", tag_dat$age, "</br>",
                      "delay:", tag_dat$delay, "</br>")

Udev <- data.frame(
  exp = c(unique(fit$tmb.data$old_tag_exp), unique(fit$tmb.data$tag_exp)),
  Udev = c(fit$rep$old_Udev, fit$rep$Udev)
)

Fay <- tidy_mat(fit$rep$F_matrix, ages = ages, years = years, value = "Fay")
names(Fay)[names(Fay) == "year"] <- "rel_year"

tag_dat <- merge(tag_dat, Udev, by = "exp")
tag_dat <- merge(tag_dat, Fay, by = c("rel_year", "age"))
tag_dat$Fsay <- tag_dat$Fay * exp(tag_dat$Udev)

## Share data across multiple plots
d <- crosstalk::SharedData$new(tag_dat, ~exp, "Select an experiment")
base <- plot_ly(d, symbol = ~period, colors = cols[1:2], symbols = c(16, 1)) %>% 
  group_by(exp) %>% 
  highlight(off = "plotly_relayout")

Row {data-height=700 .tabset}
--------------------------------------------------------------------------------

### Observed and predicted tag recaptures by experimemnt

y_ticktext <- c(50, 500, pretty(c(0, 6000), 4))
y_tickvals <- sqrt(y_ticktext)

rel_plot <- base %>%
  filter(rel_year == cap_year) %>%
  group_by(exp) %>%
  summarise(rel_year = unique(rel_year), tot_rel = sum(n_rel), period = unique(period)) %>%
  add_markers(x = ~jitter(rel_year, factor = 0.5), 
              y = ~sqrt(tot_rel), color = I(cols[1]),
              text = ~paste("exp:", exp, "</br>", "N:", tot_rel)) %>%
  layout(shapes = list(type = "line", x0 = 1996, x1 = 1996,
                       y0 = 0, y1 = 1000, yref = "y",
                       line = list(width = 1, dash = "dot")),
         yaxis = list(title = "N released",
                      tickvals = y_tickvals,
                      ticktext = y_ticktext,
                      range = range(y_tickvals)),
         xaxis = list(title = "Year"))

y_ticktext <- c(5, 20, pretty(c(0, 500), 10))
y_tickvals <- sqrt(y_ticktext)

cap_plot <- base %>%
  group_by(exp, rel_year, cap_year) %>%
  summarise(sum_pred = sum(pred), sum_obs = sum(obs),
            period = unique(period)) %>%
  group_by(exp) %>%
  add_markers(x = ~cap_year, y = ~sqrt(sum_obs), color = I(cols[1]), name = "",
              showlegend = FALSE, text = ~paste("exp:", exp, "</br>", "observed N:", sum_obs)) %>%
  add_lines(x = ~cap_year, y = ~sqrt(sum_pred), color = I(cols[2]), name = "Predicted",
            alpha = 0.7, showlegend = FALSE, symbol = NULL,
            text = ~paste("exp:", exp, "</br>", "predicted N:", round(sum_pred))) %>%
  layout(shapes = list(type = "line", x0 = 1996, x1 = 1996,
                       y0 = 0, y1 = 1000, yref = "y2",
                       line = list(width = 1, dash = "dot")),
         yaxis = list(title = "N recaptured",
                      tickvals = y_tickvals,
                      ticktext = y_ticktext,
                      range = range(y_tickvals)),
         xaxis = list(title = "Year"))

subplot(rel_plot, cap_plot, shareX = TRUE, titleX = TRUE, titleY = TRUE,
        nrows = 2, heights = c(0.3, 0.7))

> Y-axis is in square root scale

### Animation

sum_d <- tag_dat %>%
  group_by(exp, cap_year) %>%
  summarise(sum_pred = sum(pred), sum_obs = sum(obs))

sum_d %>%
  group_by(exp) %>%
  plot_ly(x = ~cap_year, frame = ~exp, hoverinfo = "x+y+text",
          showlegend = FALSE) %>%
  add_markers(y = ~sqrt(sum_obs), color = I(cols[1]),
              text = ~paste("exp:", exp, "</br>", "observed N:", sum_obs)) %>%
  add_lines(y = ~sqrt(sum_pred), color = I(cols[2]),
            text = ~paste("exp:", exp, "</br>", "predicted N:", round(sum_pred))) %>%
  animation_opts(1000, transition = 500, easing = "exp", redraw = FALSE) %>%
  layout(yaxis = list(title = "N recaptured",
                      tickvals = y_tickvals,
                      ticktext = y_ticktext,
                      range = range(y_tickvals)),
         xaxis = list(title = "Year"))

### Tag reporting rate

cov_mat <- Matrix::as.matrix(fit$tmb.data$SRR_cov_matrix)
rr <- data.frame(year = fit$tmb.data$SRR_years,
                 est = fit$tmb.data$log_SRR_est,
                 sd = sqrt(diag(cov_mat)))
rr$lwr <- rr$est - 1.96 * rr$sd
rr$upr <- rr$est + 1.96 * rr$sd
rr <- trans_est(rr)
rr$model <- "Random Walk"

ncam_rr <- data.frame(year = fit$tmb.data$SRR_years,
                      est = est$log_SRR, sd = sd$log_SRR)
ncam_rr$lwr <- ncam_rr$est - 1.96 * ncam_rr$sd
ncam_rr$upr <- ncam_rr$est + 1.96 * ncam_rr$sd
ncam_rr <- trans_est(ncam_rr)
ncam_rr$model <- "NCAM"

rr <- rbind(rr, ncam_rr)

plot_trend(rr, group = "model", col = cols, ylab = "Reporting rates", annotate = TRUE)

### Initial F deviations for tagging experiments

base %>%
  filter(rel_year == cap_year) %>%
  add_markers(x = ~rel_year, y = ~Udev, text = ~exp, color = I(cols[1]),
              showlegend = FALSE) %>%
  layout(shapes = list(type = "line", x0 = 1996, x1 = 1996,
                       y0 = min(tag_dat$Udev), y1 = max(tag_dat$Udev),
                       line = list(width = 1, dash = "dot")),
         yaxis = list(title = "Initial F deviation"),
         xaxis = list(title = "Year"))

### Observed vs. predicted recaptures

x_ticktext <- c(5, pretty(tag_dat$pred, 10))
y_ticktext <- c(5, pretty(tag_dat$obs, 10))
x_tickvals <- sqrt(x_ticktext)
y_tickvals <- sqrt(y_ticktext)

base %>%
  add_markers(x = ~sqrt(pred), y = ~sqrt(obs),
              text = ~text, color = I(cols[1]), showlegend = FALSE) %>%
  layout(shapes = list(type = "line", x0 = 0, x1 = max(sqrt(c(tag_dat$pred, tag_dat$obs))),
                       y0 = 0, y1 = max(sqrt(c(tag_dat$pred, tag_dat$obs))),
                       line = list(width = 1)),
         xaxis = list(title = "Predicted number of recaptures",
                      tickvals = x_tickvals,
                      ticktext = x_ticktext),
         yaxis = list(title = "Observed number of recaptures",
                      tickvals = y_tickvals,
                      ticktext = y_ticktext))

> Axes are in square root scale

### Standardized residuals vs. predicted recaptures

y_ticktext <- c(5, pretty(tag_dat$res, 10))
y_tickvals <- sqrt(x_ticktext)

base %>%
  add_markers( x = ~sqrt(pred), y = ~res,
               text = ~text, color = I(cols[1]), showlegend = FALSE) %>%
  layout(xaxis = list(title = "Predicted number of recaptures",
                      tickvals = x_tickvals,
                      ticktext = x_ticktext),
         yaxis = list(title = "Standardized residuals"))

> X-axis is in square root scale

Catchability
================================================================================

### Fishery selectivity

S <- apply(fit$rep$F_matrix, 2, function(x) x / max(x))
plot_surface(S, ages = ages, years = years, name = "S")

### RV survey catchability

q <- exp(fit$rep$log_RV_Qa + log(fit$tmb.data$trawl_units))
plot_surface(q, ages = ages, years = years, name = "q")

### Proportion of the stock in Smith Sound

```{r}
p <- matrix(0, nrow = length(ages), ncol = length(years),
            dimnames = list(ages, years))
ss_p <- fit$rep$SSD
ss_years <- fit$tmb.data$SS_years
ss_ages <- fit$tmb.data$SS_ages
rownames(ss_p) <- ss_ages
colnames(ss_p) <- ss_years
p[as.character(ss_ages), as.character(ss_years)] <- ss_p
plot_surface(p, ages = ages, years = years, name = "p")

### Sentinel gillnet survey catchability

log_qy <- t(replicate(length(fit$tmb.data$SN_ages), fit$rep$SN_GN_Qy))
log_qa <- fit$rep$log_SN_GN_Qa
q <- exp(log_qy + log_qa)
plot_surface(q, ages = fit$tmb.data$SN_ages,
             years = fit$tmb.data$SN_years,
             name = "q")

Trends
================================================================================

### Biomass at age

```{r}
plot_surface(fit$rep$biomass_matrix, ages = ages, years = years_plus1, name = "Biomass")
```

### Z at age

```{r}
plot_surface(fit$rep$Z_matrix, ages = ages, years = years, name = "Z")
```

### Process error (bubble plot)

```{r}
pe <- tidy_mat(fit$rep$pe, years = c(years, fit$tmb.data$proj_years)[-1],
               ages = fit$tmb.data$pe_ages, value = "res")
bubble_plot(pe)
```

Retro {`r if (is.null(fit$retro)) ".hidden"`}
================================================================================

@@

bms_plot <- trans_est(retro_tabs$log_ssb) %>%
  plot_retro(ylab = "SSB (t)", lwd = 1, col = cols[1])

abn_plot <- trans_est(retro_tabs$log_recruitment, scale = 0.001) %>%
  plot_retro(ylab = "Recruitment (age 2)", lwd = 1, col = cols[1])

blim_plot <- trans_est(retro_tabs$log_ssb_lrp) %>%
  plot_retro(ylab = "SSB/Blim", lwd = 1, col = cols[1]) %>%
  add_segments(x = min_year, xend = max_year + 1, y = 1, yend = 1, color = I("black"),
               linetype = I(3), name = "Blim", text = NULL, hoverinfo = "none")

@@

bms_plot <- trans_est(retro_tabs$log_ssb) %>%
  plot_mohns(col = cols[1], ylab = "SSB")

abn_plot <- trans_est(retro_tabs$log_recruitment, scale = 0.001) %>%
  plot_mohns(ylab = "Recruitment (age 2)", col = cols[1])

blim_plot <- trans_est(retro_tabs$log_ssb_lrp) %>%
  plot_mohns(ylab = "SSB/Blim", col = cols[1])

@@

bms_plot <- retro_tabs$log_ssb %>%
  plot_retro_deltas(in_col = cols[1], ylab = "log(SSB)")

abn_plot <- retro_tabs$log_recruitment %>%
  plot_retro_deltas(ylab = "log(Recruitment)", in_col = cols[1])

blim_plot <- retro_tabs$log_ssb_lrp %>%
  plot_retro_deltas(ylab = "log(SSB/Blim)", in_col = cols[1])

@@

z_plot <- trans_est(retro_tabs$log_aveZ) %>%
  plot_retro(ylab = "Average Z (ages 5+)", lwd = 1, col = cols[1])

m_plot <- trans_est(retro_tabs$log_aveM) %>%
  plot_retro(ylab = "Average M (ages 5+)", lwd = 1, col = cols[1])

f_plot <- trans_est(retro_tabs$log_aveF) %>%
  plot_retro(ylab = "Average F (ages 5+)", lwd = 1, col = cols[1])

@@

z_plot <- trans_est(retro_tabs$log_aveZ) %>%
  plot_mohns(ylab = "Average Z (ages 5+)", col = cols[1])

m_plot <- trans_est(retro_tabs$log_aveM) %>%
  plot_mohns(ylab = "Average M (ages 5+)", col = cols[1])

f_plot <- trans_est(retro_tabs$log_aveF) %>%
  plot_mohns(ylab = "Average F (ages 5+)", col = cols[1])

@@

z_plot <- retro_tabs$log_aveZ %>%
  plot_retro_deltas(ylab = "log(Average Z)", in_col = cols[1])

m_plot <- retro_tabs$log_aveM %>%
  plot_retro_deltas(ylab = "log(Average M)", in_col = cols[1])

f_plot <- retro_tabs$log_aveF %>%
  plot_retro_deltas(ylab = "log(Average F)", in_col = cols[1])

@@

Comps {`r if (is.null(tmp$comp)) ".hidden"`}
================================================================================

@@

Productivity
================================================================================

>>>>

Retro {data-navmenu="Trends" `r if (is.null(fit$retro)) ".hidden"`}
================================================================================

@@

bms_plot <- trans_est(retro_tabs$log_ssb) %>%
  plot_retro(ylab = "SSB (t)", lwd = 1, col = pred_col)

abn_plot <- trans_est(retro_tabs$log_recruitment, scale = 0.001) %>%
  plot_retro(ylab = "Recruitment (age 2)", lwd = 1, col = pred_col)

blim_plot <- trans_est(retro_tabs$log_ssb_lrp) %>%
  plot_retro(ylab = "SSB/Blim", lwd = 1, col = pred_col) %>%
  add_segments(x = min_year, xend = max_year + 1, y = 1, yend = 1, color = I("black"),
               linetype = I(3), name = "Blim", text = NULL, hoverinfo = "none")

@@

bms_plot <- trans_est(retro_tabs$log_ssb) %>%
  plot_mohns(col = pred_col, ylab = "SSB")

abn_plot <- trans_est(retro_tabs$log_recruitment, scale = 0.001) %>%
  plot_mohns(ylab = "Recruitment (age 2)", col = pred_col)

blim_plot <- trans_est(retro_tabs$log_ssb_lrp) %>%
  plot_mohns(ylab = "SSB/Blim", col = pred_col)

@@

bms_plot <- retro_tabs$log_ssb %>%
  plot_retro_deltas(in_col = pred_col, ylab = "log(SSB)")

abn_plot <- retro_tabs$log_recruitment %>%
  plot_retro_deltas(ylab = "log(Recruitment)", in_col = pred_col)

blim_plot <- retro_tabs$log_ssb_lrp %>%
  plot_retro_deltas(ylab = "log(SSB/Blim)", in_col = pred_col)

@@

z_plot <- trans_est(retro_tabs$log_aveZ) %>%
  plot_retro(ylab = "Average Z (ages 5+)", lwd = 1, col = pred_col)

m_plot <- trans_est(retro_tabs$log_aveM) %>%
  plot_retro(ylab = "Average M (ages 5+)", lwd = 1, col = pred_col)

f_plot <- trans_est(retro_tabs$log_aveF) %>%
  plot_retro(ylab = "Average F (ages 5+)", lwd = 1, col = pred_col)

@@

z_plot <- trans_est(retro_tabs$log_aveZ) %>%
  plot_mohns(ylab = "Average Z (ages 5+)", col = pred_col)

m_plot <- trans_est(retro_tabs$log_aveM) %>%
  plot_mohns(ylab = "Average M (ages 5+)", col = pred_col)

f_plot <- trans_est(retro_tabs$log_aveF) %>%
  plot_mohns(ylab = "Average F (ages 5+)", col = pred_col)

@@

z_plot <- retro_tabs$log_aveZ %>%
  plot_retro_deltas(ylab = "log(Average Z)", in_col = pred_col)

m_plot <- retro_tabs$log_aveM %>%
  plot_retro_deltas(ylab = "log(Average M)", in_col = pred_col)

f_plot <- retro_tabs$log_aveF %>%
  plot_retro_deltas(ylab = "log(Average F)", in_col = pred_col)

@@

Comps {data-navmenu="Trends" `r if (is.null(tmp$comp)) ".hidden"`}
================================================================================

@@

Status and rates {data-navmenu="Trends"}
================================================================================

<!-- ### Biomass at age -->

<!-- ```{r} -->
<!-- plot_surface(fit$rep$biomass_matrix, ages = ages, years = years_plus1, name = "Biomass") -->
<!-- ``` -->

### Demographics

a <- tidy_mat(fit$rep$N_matrix * 1000, ages = ages, years = years_plus1, value = "abundance") %>% 
  dplyr::left_join(trans_est(tabs$log_abundance, scale = 0.001), by = "year") %>% 
  rename(tot_abundance = est, tot_abundance_lwr = lwr, tot_abundance_upr = upr,
         tot_abundance_sd = sd)

b <- tidy_mat(fit$rep$biomass_matrix, ages = ages, years = years_plus1, value = "biomass") %>% 
  dplyr::left_join(trans_est(tabs$log_biomass), by = "year") %>% 
  rename(tot_biomass = est, tot_biomass_lwr = lwr, tot_biomass_upr = upr,
         tot_biomass_sd = sd)

c <- tidy_mat(fit$rep$ssb_matrix, ages = ages, years = years_plus1, value = "ssb") %>% 
  dplyr::left_join(trans_est(tabs$log_ssb), by = "year") %>% 
  dplyr::rename(tot_ssb = est, tot_ssb_lwr = lwr, tot_ssb_upr = upr,
                tot_ssb_sd = sd)

d <- dplyr::left_join(a, b, by = c("year", "age")) %>%
  dplyr::left_join(c, by = c("year", "age")) %>%
  mutate(cohort = year - age,
         abundance_prop = abundance / tot_abundance,
         abundance_lab = paste0("Abundance<br>", 
                                ifelse(gsub("[[:digit:]]", "", text_units(tot_abundance_lwr)) ==
                                         gsub("[[:digit:]]", "", text_units(tot_abundance_upr)),
                                       gsub("[[:alpha:]]", "", text_units(tot_abundance_lwr)),
                                       text_units(tot_abundance_lwr)), "-", 
                                text_units(tot_abundance_upr)),
         biomass_prop = -(biomass / tot_biomass),
         biomass_lab = paste0("Biomass<br>", 
                              ifelse(gsub("[[:digit:]]", "", text_units(tot_biomass_lwr)) ==
                                       gsub("[[:digit:]]", "", text_units(tot_biomass_upr)),
                                     gsub("[[:alpha:]]", "", text_units(tot_biomass_lwr)),
                                     paste0(text_units(tot_biomass_lwr), "t")), "-", 
                              text_units(tot_biomass_upr), "t"),
         ssb_prop = -(ssb / tot_ssb),
         ssb_lab = paste0("SSB<br>", 
                          ifelse(gsub("[[:digit:]]", "", text_units(tot_ssb_lwr)) ==
                                   gsub("[[:digit:]]", "", text_units(tot_ssb_upr)),
                                 gsub("[[:alpha:]]", "", text_units(tot_ssb_lwr)),
                                 paste0(text_units(tot_ssb_lwr), "t")), "-", 
                          text_units(tot_ssb_upr), "t")) %>%
  arrange(year, age)

max_x <- max(c(d$abundance_prop, d$biomass_prop)) * 1.2
xlabs <- pretty(c(-max_x, max_x), n = 10)

rec <- fit$rep$N_matrix[1, ]
rec_spikes <- find_peaks(rec, m = 1)
rec_spikes <- years[rec_spikes] - min(ages)
